%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Product Manager (Senior Generalist – Growth \& Product)} % Job title
    {Skylight Tools Inc.} % Organization
    {} % Location
    {2019 - 2020} % Date(s)
    {
    \setlist[itemize,2]{label=\textopenbullet}
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created stakeholder consensus across the organization’s leadership and various teams, projecting the value-added by launching new product offerings and limiting scope
            \begin{itemize}[leftmargin=*]
                \item {Skylight Recommended reduced the time it takes to begin construction by up to 4 weeks or 25\% compared to our standard offering. Thereby, offering our clients a fast and easy renovation process.}
                \item {Operationalized our Material Bank partnership allowing us to deliver renovation material samples to a client’s home overnight.
                \newline This partnership will eventually lead to eliminate the need for clients to visit any showrooms.}
            \end{itemize}
        \item {Streamlined the product execution process for our clients and internal teams allowing for an increase in capacity of concurrent projects
            \begin{itemize}[leftmargin=*]
                \item {Improved the client deliverable definitions of our renovation visualizations. Through this funnel iteration, we delivered faster turnaround times for the 3D renders of a proposed renovation. Improving key KPIs.}
            \end{itemize}}
        \item {Developed analytics dashboards based on critical KPIs to visualize project P\&L}
        \item {Converged internal data sources to forecast future material sample orders based on projected growth and demand}}
    \end{cvitems}
    }
    {
    \begin{cventrysummary}
    Skylight is focused on using technology to reimagine the home renovation experience. At Skylight I worked with the management team to create new sales channels, internal processes, and launch new product offerings.
    \end{cventrysummary}
    }
    
%---------------------------------------------------------
  \cventry
    {Product Lead \& Co-Founder} % Job title
    {SWFTCharge Inc.
   \textit{\textcolor{awesome}{(Successfully Exited)}}
    } % Organization
    {} % Location
    {2016 - 2018} % Date(s)
    {
    \setlist[itemize,2]{label=\textopenbullet}
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and launched a service focused on eliminating battery anxiety at large scale events (Electric Forest, Coachella, Lost Lands, Boots \& Hearts, etc.)
        \begin{itemize}[leftmargin=*]
            \item {SWFTCharge provides access to wire free charging devices that allow users to keep their phones charged throughout the duration of a multiday event}
        \end{itemize}
        \item {Continuously adapted the business model and the service based on customer needs as well as stakeholder requirements}
        \item {Negotiated multi-year exclusive contracts with multinational corporations that operate events to secure our sales channel}
        \item {Increased revenue 6x YOY using the resources secured through the funding round}
        \item {Created the logistics and operations roadmap to support events happening concurrently across North America}}
    \end{cvitems}
    }
    {
    \begin{cventrysummary}
        I launched and led this venture from the time it was a product focused company to our pivot into a service based company. We recognized the market need after conducting hundreds of customer interviews and executed plans to launch our self-funded MVP in Canada. After generating significant revenues through our MVP, I led our funding round to raise \$500,000 through angel investors to expand the company across various music festivals in North America and beyond.
    \end{cventrysummary} 
    }
%---------------------------------------------------------
\end{cventries}
